%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Simple LaTeX CV Template %%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% NOTE: If you find that it says                                     %%
%%                                                                    %%
%%                           1 of ??                                  %%
%%                                                                    %%
%% at the bottom of your first page, this means that the AUX file     %%
%% was not available when you ran LaTeX on this source. Simply RERUN  %% 
%% LaTeX to get the ``??'' replaced with the number of the last page  %% 
%% of the document. The AUX file will be generated on the first run   %%
%% of LaTeX and used on the second run to fill in all of the          %%
%% references.                                                        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%% Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't like 10pt? Try 11pt or 12pt
\documentclass[11pt]{article} 

% This is a helpful package that puts math inside length specifications
\usepackage{calc}
\usepackage{textcomp}
\usepackage{amssymb}

% Layout: Puts the section titles on left side of page
\reversemarginpar

%
%         PAPER SIZE, PAGE NUMBER, AND DOCUMENT LAYOUT NOTES:
%
% The next \usepackage line changes the layout for CV style section
% headings as marginal notes. It also sets up the paper size as either
% letter or A4. By default, letter was used. If A4 paper is desired,
% comment out the letterpaper lines and uncomment the a4paper lines.
%
% As you can see, the margin widths and section title widths can be
% easily adjusted.
%
% ALSO: Notice that the includefoot option can be commented OUT in order
% to put the PAGE NUMBER *IN* the bottom margin. This will make the
% effective text area larger.
%
% IF YOU WISH TO REMOVE THE ``of LASTPAGE'' next to each page number,
% see the note about the +LP and -LP lines below. Comment out the +LP
% and uncomment the -LP.
%
% IF YOU WISH TO REMOVE PAGE NUMBERS, be sure that the includefoot line
% is uncommented and ALSO uncomment the \pagestyle{empty} a few lines
% below.
%

%% Use these lines for letter-sized paper
\usepackage[paper=letterpaper,
            %includefoot, % Uncomment to put page number above margin
            marginparwidth=1.2in,     % Length of section titles
            marginparsep=.05in,       % Space between titles and text
            margin=1in,               % 1 inch margins
            includemp]{geometry}

%% Use these lines for A4-sized paper
%\usepackage[paper=a4paper,
%            %includefoot, % Uncomment to put page number above margin
%            marginparwidth=30.5mm,    % Length of section titles
%            marginparsep=1.5mm,       % Space between titles and text
%            margin=25mm,              % 25mm margins
%            includemp]{geometry}

%% More layout: Get rid of indenting throughout entire document
\setlength{\parindent}{0in}

%% This gives us fun enumeration environments. compactitem will be nice.
\usepackage{paralist}

%% Reference the last page in the page number
%
% NOTE: comment the +LP line and uncomment the -LP line to have page
%       numbers without the ``of ##'' last page reference)
%
% NOTE: uncomment the \pagestyle{empty} line to get rid of all page
%       numbers (make sure includefoot is commented out above)
%
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
%\pagestyle{empty}      % Uncomment this to get rid of page numbers
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\fancyfootoffset{\marginparsep+\marginparwidth}
\newlength{\footpageshift}
\setlength{\footpageshift}
          {0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}
\lfoot{\hspace{\footpageshift}%
       \parbox{4in}{\, \hfill %
                    \arabic{page} of \protect\pageref*{LastPage} % +LP
%                    \arabic{page}                               % -LP
                    \hfill \,}}

% Finally, give us PDF bookmarks
\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}

% for \textcopyright, \textregistered and \texttrademark
\usepackage{textcomp}

% for printing last update time
\usepackage{datetime}

%%%%%%%%%%%%%%%%%%%%%%%% End Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%% Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newenvironment{narrow}[2]{%
\begin{list}{}{%
\setlength{\topsep}{0pt}%
\setlength{\leftmargin}{#1}%
\setlength{\rightmargin}{#2}%
\setlength{\listparindent}{\parindent}%
\setlength{\itemindent}{\parindent}%
\setlength{\parsep}{\parskip}%
}%
\item[]}{\end{list}} 

% The title (name) with a horizontal rule under it
%
% Usage: \makeheading{name}
%
% Place at top of document. It should be the first thing.
\newcommand{\makeheading}[1]%
        {\hspace*{-\marginparsep minus \marginparwidth}%
         \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
                {\large \bfseries #1}\\[-0.15\baselineskip]%
                 \rule{\columnwidth}{1pt}%
         \end{minipage}}

% The section headings
%
% Usage: \section{section name}
%
% Follow this section IMMEDIATELY with the first line of the section
% text. Do not put whitespace in between. That is, do this:
%
%       \section{My Information}
%       Here is my information.
%
% and NOT this:
%
%       \section{My Information}
%
%       Here is my information.
%
% Otherwise the top of the section header will not line up with the top
% of the section. Of course, using a single comment character (%) on
% empty lines allows for the function of the first example with the
% readability of the second example.
\renewcommand{\section}[2]%
        {\pagebreak[2]\vspace{1.3\baselineskip}%
         \phantomsection\addcontentsline{toc}{section}{#1}%
         \hspace{0in}%
         \marginpar{
         \raggedright \scshape #1}#2}


% An itemize-style list with lots of space between items
\newenvironment{outerlist}[1][\enskip\textbullet]%
        {\begin{itemize}[#1]}{\end{itemize}%
         \vspace{-.6\baselineskip}}

% An environment IDENTICAL to outerlist that has better pre-list spacing
% when used as the first thing in a \section 
\newenvironment{lonelist}[1][\enskip\textbullet]%
        {\vspace{-\baselineskip}\begin{list}{#1}{%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{list}\vspace{-.6\baselineskip}}

\newenvironment{king}
{\rule{1ex}{1ex}%
\hspace{\stretch{1}}}
{\hspace{\stretch{1}}%
\rule{1ex}{1ex}}


% An itemize-style list with little space between items
\newenvironment{innerlist}[1][\enskip\textbullet]%
        {\begin{compactitem}[#1]}{\end{compactitem}}

% To add some paragraph space between lines.
% This also tells LaTeX to preferably break a page on one of these gaps
% if there is a needed pagebreak nearby.
\newcommand{\blankline}{\quad\pagebreak[2]}

%%%%%%%%%%%%%%%%%%%%%%%% End Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%% Begin CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\makeheading{Shanbo Li}

\section{Contact Information}
%
% NOTE: Mind where the & separators and \\ breaks are in the following
%       table.
%
% ALSO: \rcollength is the width of the right column of the table \textasciitilde
%       (adjust it to your liking; default is 1.85in).
%
\newlength{\rcollength}\setlength{\rcollength}{3.2in}%
%

\textit{Tel:}  +86 13810559910 \\
\textit{E-mail:} \href{mailto:shanboli@gmail.com}{shanboli@gmail.com}\\
\textit{Homepage:} \href{http://www.borntojava.com/}{www.borntojava.com}\\
\textit{LinkedIn:} \href{http://cn.linkedin.com/in/shanboli}{cn.linkedin.com/in/shanboli}

\section{Nationality}
%
Chinese

\section{Data of birth}
%
1984-08-10

\section{Gender}
%
male

\section{Education}
%
\href{http://www.kth.se/}{\textbf{Royal Institute of Technology /\\ Kungliga Tekniska H\"{o}gskolan (KTH)}},\\ 
\textbf{Stockholm, Sweden}
\begin{outerlist}
\item[] Master's Degree,\\ 
        {Software Engineering of Distributed Systems} \\
        September 2007 - September 2009
\item[] Thesis: \href{http://shanbohomepage.googlecode.com/hg/master_thesis/master_thesis.pdf}{Web Call Example Application}
\end{outerlist}
\blankline

\href{http://www.njtu.edu.cn/en/}{\textbf{Beijing Jiaotong University}},\\
\textbf{Beijing, China}
\begin{outerlist}
\item[] 4-year Bachelor's Degree in Engineering, \\
        {Computer Science}\\
        September 2003 - June 2007
\end{outerlist}       

%
\section{Working Experience}
\href{http://www.ericsson.com/cn}{\textbf{Ericsson (China) CO., LTD.}}, {DUIB China}
\begin{outerlist}
\item[] \textit{Team Leader, Software Design Engineer}%
        \hfill \textbf{January 2010 to Now}
\begin{outerlist}
\item \textit{Responsibility:}\\
Handle feature requests and bug reports for the project.
Prioritize and assign trackers to team members.
Cooperate tasks in global distributed teams with developers from different culture. Quality control and coding. Drive support forum to help customers. 
Mentor for newcomers.
\end{outerlist}
\end{outerlist}
\blankline

\href{http://www.ericsson.com/cn}{\textbf{Ericsson (China) CO., LTD.}}, {DUIB China}
\begin{outerlist}
\item[] \textit{Software Engineer}%
        \hfill \textbf{September 2009 to December 2009}
\begin{outerlist}
\item \textit{Responsibility:}\\
Implement assigned tasks. Analyze the root cause and fix bugs.
Refine projects. Communicate with customers, understand their requirements and implemented their feature requests. Support customers via forum and email, analyze their logs and help them to find the issues.
\end{outerlist}
\end{outerlist}
\blankline

%
\href{http://www.ericsson.com/cn}{\textbf{Ericsson (China) CO., LTD.}}, {System Integration and Verification}
\begin{outerlist}

\item[] \textit{Intern, Software Developer}%
        \hfill \textbf{March 2009 to September 2009}
\begin{outerlist}
\item \textit{Responsibility:}\\
Implement assigned tasks. Analyze the root cause and fix bugs.
Refine projects.
\end{outerlist}
\end{outerlist}
\blankline

%
\href{http://www.ericsson.com/}{\textbf{Ericsson AB}}, \href{http://www.ericsson.com/developer}{Ericsson Developer Connection} ,
Sweden
\begin{outerlist}

\item[] \textit{Java Programmer}%
        \hfill \textbf{March 2008 to March 2009}

\item[] {\textbf{Web Call SDK}}
\begin{outerlist}
\item \textit{Responsibility:}\\
Pre-study, Establish Theory, Design, Implement and Test. 
\item \textit{Thesis:}\\
\href{http://shanbohomepage.googlecode.com/hg/master_thesis/master_thesis.pdf}{Web Call Example Application}
\end{outerlist}
\end{outerlist}
\blankline


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Awards %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Award}
\textbf{Ericsson Excellent Team}
\begin{outerlist}
\item[] \href{http://www.ericsson.com/}{\textit{Ericsson China R\&D}}
        \hfill \textbf{2010}
\end{outerlist}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Professional Trainings %%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Trainings}
\textbf{Exerting the Influence in Project Management}
\begin{outerlist}
\item[] \href{http://www.ericssonacademy.com/}{\textit{Ericsson Academy, China}}
        \hfill \textbf{June 2011}
\end{outerlist}
\blankline

\textbf{On The Way To Lead}
\begin{outerlist}
\item[] \href{http://www.ericssonacademy.com/}{\textit{Ericsson Academy, China}}
        \hfill \textbf{June 2010}
\end{outerlist}
\blankline

\textbf{Manager Recruitment Training}
\begin{outerlist}
\item[] \href{http://www.ericssonacademy.com/}{\textit{Ericsson Academy, China}}
        \hfill \textbf{May 2010}
\end{outerlist}
\blankline

\textbf{Effective Java and Design Patterns}
\begin{outerlist}
\item[] \href{http://www.informator.se/}{\textit{Informator, Sweden}}
        \hfill \textbf{February 2010}
\end{outerlist}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Social Skills %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Social Skills}
{\textbf{Strong leader and full of team spirit}}\\
{\textbf{Excellent communicator}}\\
{\textbf{Travel on demand}}\\
{\textbf{Cope with pressure}}\\
{\textbf{Willing to learn new technology}}\\
{\textbf{Fluent in English and Chinese}}\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Knowledge Areas %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Knowledge Areas}
{\textbf{Web 2.0 and cutting-edge technologies}}\\
{\textbf{Problem identify and resolve}}\\
{\textbf{Distributed systems}}\\ 
{\textbf{Network security}}\\ 
{\textbf{OSI Model and network communication protocols}}\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Professional Skills%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Professional Skills} 
%
{\textbf{8 Years of Java Programming Experience:}}\\
Expert at Java EE/ Java SE/ Java ME

\blankline

{\textbf{4 Years of Ruby \nolinebreak on \nolinebreak Rails Experience:}}\\
Expert at 
\href{http://www.ruby-lang.org/en/}{Ruby}, 
\href{http://rubyonrails.org/}{Ruby on Rails} and RoR plugin hacking

\blankline

{\textbf{Database development and Management:}}\\
\href{http://www.mysql.com/}{MySQL}, 
\href{http://www.oracle.com/us/products/database/index.html}{Oracle Database}, 
\href{http://memcached.org/}{Memcached} and knowledge of NoSQL

\blankline

{\textbf{Java Frameworks:}}\\
JSF, Hibernate, EJB, Spring, Struts, GWT, Swing, JUnit, TestNG, Log4j, SLF4J

\blankline

{\textbf{Ruby \nolinebreak on \nolinebreak Rails plugin:}}\\
\href{http://activescaffold.com/}{ActiveScaffold},
Restful Authentication,
Cache Money,
Seed Fu

\blankline

{\textbf{Skill set of Web Services development:}}\\
SOAP, WSDL, UDDI, BPEL, Metro, AXIS, RESTful Web Service


\blankline

{\textbf{Skill set of Web Site development:}}\\
XHTML, XHTML MP, HTML, CSS, XML, Javascript, JSON, AJAX, JSP, PHP 

\blankline

{\textbf{Application Server:}}\\
Apache Tomcat, Jetty, Glassfish, JBoss, 
\href{http://nginx.net/}{nginx}, Apache HTTP Server

\blankline

{\textbf{Software Development Concept:}}\\
Agile Software Development 
(\href{http://en.wikipedia.org/wiki/Scrum_\%28development\%29}{Scrum}, 
\href{http://www.extremeprogramming.org/}{Extreme Programming}), Object-oriented Programming, UML, Design \nolinebreak Patterns

\blankline

{\textbf{Project management and team collaboration tools:}}\\
\href{http://maven.apache.org/}{Apache Maven},
\href{http://ant.apache.org/}{Apache Ant}, 
\href{http://git-scm.com/}{Git}, \href{http://www-01.ibm.com/software/awdtools/clearcase/index.html}{Rational\textregistered\space ClearCase (Base ClearCase and ClearCase UCM)},
\href{http://mercurial.selenic.com/}{Mercurial},
\href{http://subversion.tigris.org/}{Subversion}, 
\href{http://www.nongnu.org/cvs/}{CVS},
\href{http://jenkins-ci.org/}{Jenkins/Hudson},
\href{http://www.open.collab.net/products/ctf/}{CollabNet TeamForge},
\href{https://jazz.net/projects/rational-team-concert/}{Rational Team Concert}

\blankline

{\textbf{Development Tools:}}\\
\href{http://www.jetbrains.com/idea/}{IntelliJ\textregistered\space IDEA},
\href{http://www.jetbrains.com/ruby}{RubyMine\texttrademark},
\href{http://www.eclipse.org/}{Eclipse},
\href{http://netbeans.org/}{NetBeans IDE}, \\
\href{http://www.ibm.com/developerworks/rational/products/rsa/}{IBM\textregistered\space Rational\textregistered\space Software Architect (RSA)},
\href{http://www.embarcadero.com/products/jbuilder}{JBuilder}

\blankline

{\textbf{Other Programming Experience:}}\\
C/C++, PHP, Erlang, Prolog, DOT language

\blankline

{\textbf{Documentation Tools:}}\\ 
Microsoft Office, iWork, \LaTeX{}, 
and other common productivity packages for Windows, Mac\nolinebreak\space OS\nolinebreak\space X, and
Linux platforms

\blankline

{\textbf{Operating Systems:}}\\
Windows, Linux, Unix, Mac OS X

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Commercial Projects %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Commercial Projects}
\textbf{JCAT(Java Common Automation Test)}
\hfill \textbf{March 2009 to Now}
\begin{outerlist}
\item \textit{Role:}\\
Team Leader (intern, team member in the beginning)
\item \textit{Project Description:}\\
A bundle of Java applications for automation test, statistics and report. It is widely used in the three major platforms (CPP, TSP, AXE) of Ericsson on integration and verification.
\item \textit{Language and Frameworks:}\\
Java SE, Java EE, JUnit, TestNG, MySQL
\end{outerlist}
\blankline

\textbf{Ericsson China Recruiting System (Internal)}
\hfill \textbf{August 2010 to Now}
\begin{outerlist}
\item \textit{Role:}\\
Architect and main developer
\item \textit{Responsibility:}\\
Communicate with Ericsson China recruiting team and understand their requirements about a recruiting system for internal use. Independenctly design and implement the Ruby on Rail based recruiting and interview arrange system.
\item \textit{Project Description:}\\
A recruiting system for HR department internal use. Which includes application management, interview arrangement, duplicated applications checking, r\'{e}sum\'{e} management, data import and export, etc. 
\item \textit{Language and Frameworks:}\\
Ruby on Rails, 
\href{http://activescaffold.com/}{ActiveScaffold},
\href{http://memcached.org/}{Memcached}, MySQL, 
\href{http://nginx.net/}{nginx}, 
\href{http://www.modrails.com/}{Phusion \nobreak Passenger\texttrademark}
\end{outerlist}
\blankline

\textbf{Web Call SDK}
\hfill \textbf{March 2008 to March 2009}
\begin{outerlist}
\item \textit{Role:}\\
Architecture and main developer
\item \textit{Description:}\\
A Java EE web application for making VoIP calls. It supplies both browser client and Java ME client. 
\item \textit{Technologies:}\\
IMS, VoIP, SIP, SDP, 3PCC, Web Application, Web Service, MIDlet
\item \textit{Language and Frameworks:}\\
Java EE, Metro, MjSIP, JMF, Mobile Front Controller, JSR\nobreak\space 172, JSR\nobreak\space 75,\\ Tomcat, MySQL
\item \textit{Thesis:}\\
\href{http://shanbohomepage.googlecode.com/hg/master_thesis/master_thesis.pdf}{Web Call Example Application}
\end{outerlist}
\blankline

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% OpenSource Projects %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{OpenSource Projects}
\href{http://code.google.com/p/scallope/}{\textbf{Scallope}} 
\begin{outerlist}
\item \texttt{Description:}
A application acts as a web client login to sip provider's web page and make VoIP calls. 
\item \texttt{Language and Frameworks:}
Java, Apache common HTTP.
\item \texttt{Homepage:}
\href{http://code.google.com/p/scallope/}{http://code.google.com/p/scallope/}
\end{outerlist}

\blankline

\href{http://code.google.com/p/mobilecurrencyconverter/}{\textbf{Mobile Currency Converter}} 
\begin{outerlist}
\item \texttt{Description:}
A Java ME currency converter. It fetches the latest currency exchange rate from Google Finance. 
\item \texttt{Language and Frameworks:}
Java ME
\item \texttt{Homepage:}
\href{http://code.google.com/p/mobilecurrencyconverter/}{http://code.google.com/p/mobilecurrencyconverter/}
\end{outerlist}

\section{Academic Projects}
\textbf{Bouncer}, KTH, Sweden \hfill \textbf{March 2008 to May 2008}
\begin{innerlist}
\item \texttt{Description:}
A Packet bouncer that "bounces" connections from one machine to another.
\item \texttt{Language and Frameworks:}
Java, Jpcap
\end{innerlist}

\blankline

\textbf{SIP Speaker}, KTH, Sweden \hfill \textbf{March 2008 to May 2008}
\begin{outerlist}
\item \texttt{Description:}
A SIP user agent (UA) that waits for incoming calls and answers them when received.
\item \texttt{Language and Frameworks:}
Java, JMF, FreeTTS
\end{outerlist}

\blankline

\textbf{Web Mail}, KTH, Sweden \hfill \textbf{March 2008 to May 2008}
\begin{outerlist}
\item \texttt{Description:}
A web server for sending e-mails. No 3rd party library.
\item \texttt{Language and Frameworks:}
Java
\end{outerlist}

\blankline

\textbf{Flight Ticket Reservation}, KTH, Sweden \hfill \textbf{January 2008 to March 2008}
\begin{outerlist}
\item \texttt{Description:}
A web service for booking flight tickets.
\item \texttt{Language and Frameworks:}
Java EE, JSF, Web Service (Metro), BPEL, JPA, MySQL 
\end{outerlist}

\blankline

\textbf{E-Shop}, KTH, Sweden \hfill \textbf{November 2007 to January 2008}
\begin{outerlist}
\item \texttt{Description:}
A web shop
\item \texttt{Language and Frameworks:}
Java EE, Struts, MySQL
\end{outerlist}

\blankline

\textbf{Forex}, KTH, Sweden \hfill \textbf{November 2007 to January 2008}
\begin{outerlist}
\item \texttt{Description:}
A web site for checking currency exchange rate
\item \texttt{Language and Frameworks:}
Java EE, JSF, EJB3
\end{outerlist}

\blankline

\textbf{iAd}, KTH, Sweden \hfill \textbf{November 2007 to January 2008}
\begin{outerlist}
\item \texttt{Description:}
A resource management system for advertisment company, which is developed by the method of Extreme Programming.
\item \texttt{Language and Frameworks:}
Ruby on Rails, MySQL
\end{outerlist}

\blankline

\textbf{Database course web site}, BJTU, China \hfill \textbf{January 2007 to June 2007}
\begin{outerlist}
\item \texttt{Description:}
A online CAI system used to do online question, upload homework, check homework and manage student infomation.
\item \texttt{Language and Frameworks:}
Ruby on Rails, MySQL
\end{outerlist}

\blankline

\textbf{Anti-Counterfeiting}, BJTU, China \hfill \textbf{September 2006 to January 2007}
\begin{outerlist}
\item \texttt{Description:}
A online anti-counterfeiting system
\item \texttt{Language and Frameworks:}
Java, Struts, Spring, Hibernate, MySQL
\end{outerlist}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Footer %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\vfill
\begin{narrow}{0.15in}{1.5in}
\begin{center}
\begin{footnotesize}
\begin{center}
Last updated: \today 
\end{center}
\href{http://www.borntojava.com/CV.pdf}{\tt http://www.borntojava.com/CV.pdf}
\end{footnotesize}\\
\vspace{0.2in}
\textit{Produced by \LaTeX}
\end{center}
\end{narrow}

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%% End CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
