\makeheading{Shanbo Li}

\section{Contact Information}
%
% NOTE: Mind where the & separators and \\ breaks are in the following
%       table.
%
% ALSO: \rcollength is the width of the right column of the table \textasciitilde
%       (adjust it to your liking; default is 1.85in).
%
\newlength{\rcollength}\setlength{\rcollength}{3.2in}%
%
Tel: \textsf{+86 13810559910} \\
E-mail: \href{mailto:shanboli@gmail.com}{shanboli@gmail.com}\\
Homepage: \href{http://www.borntojava.com/}{http://www.borntojava.com}\\
LinkedIn: \href{http://cn.linkedin.com/in/shanboli}{http://cn.linkedin.com/in/shanboli}\\
Latest CV:
\href{http://shanboli.info/}{http://shanboli.info}

\section{Nationality}
%
Chinese

\section{Data of birth}
%
1984-08-10

\section{Gender}
%
male

\section{Education}
%
\href{http://www.kth.se/}{\textbf{Royal Institute of Technology /\\ Kungliga Tekniska H\"{o}gskolan (KTH)}},\\ 
\textbf{Stockholm, Sweden}
\begin{outerlist}
\item[] Master's Degree,\\ 
        {Software Engineering of Distributed Systems} \\
        September 2007 - September 2009
\item[] Thesis: \href{http://shanbohomepage.googlecode.com/hg/master_thesis/master_thesis.pdf}{Web Call Example Application}
\end{outerlist}
\blankline

\href{http://www.njtu.edu.cn/en/}{\textbf{Beijing Jiaotong University}},\\
\textbf{Beijing, China}
\begin{outerlist}
\item[] 4-year Bachelor's Degree in Engineering, \\
        {Computer Science}\\
        September 2003 - June 2007
\end{outerlist}       

%
\section{Working Experience}
\href{http://www.ericsson.com/cn}{\textbf{Ericsson (China) CO., LTD.}}, {DUIB China}
\begin{outerlist}
\item[] \textit{Team Leader, Software Design Engineer}%
        \hfill \textbf{January 2010 to Now}
\begin{outerlist}
\item \textit{Responsibility:}\\
Handle feature requests and bug reports for the project.
Prioritize and assign trackers to team members.
Cooperate tasks in global distributed teams with developers from different culture. Quality control and coding. Drive support forum to help customers. 
Mentor for newcomers.
\end{outerlist}
\end{outerlist}
\blankline

\href{http://www.ericsson.com/cn}{\textbf{Ericsson (China) CO., LTD.}}, {DUIB China}
\begin{outerlist}
\item[] \textit{Software Engineer}%
        \hfill \textbf{September 2009 to December 2009}
\begin{outerlist}
\item \textit{Responsibility:}\\
Implement assigned tasks. Analyze the root cause and fix bugs.
Refine projects. Communicate with customers, understand their requirements and implemented their feature requests. Support customers via forum and email, analyze their logs and help them to find the issues.
\end{outerlist}
\end{outerlist}
\blankline

%
\href{http://www.ericsson.com/cn}{\textbf{Ericsson (China) CO., LTD.}}, {System Integration and Verification}
\begin{outerlist}

\item[] \textit{Intern, Software Developer}%
        \hfill \textbf{March 2009 to September 2009}
\begin{outerlist}
\item \textit{Responsibility:}\\
Implement assigned tasks. Analyze the root cause and fix bugs.
Refine projects.
\end{outerlist}
\end{outerlist}
\blankline

%
\href{http://www.ericsson.com/}{\textbf{Ericsson AB}}, \href{http://www.ericsson.com/developer}{Ericsson Developer Connection} ,
Sweden
\begin{outerlist}

\item[] \textit{Java Programmer}%
        \hfill \textbf{March 2008 to March 2009}

\item[] {\textbf{Web Call SDK}}
\begin{outerlist}
\item \textit{Responsibility:}\\
Pre-study, Establish Theory, Design, Implement and Test. 
\item \textit{Thesis:}\\
\href{http://shanbohomepage.googlecode.com/hg/master_thesis/master_thesis.pdf}{Web Call Example Application}
\end{outerlist}
\end{outerlist}
\blankline


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Awards %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Award}
\textbf{Ericsson Excellent Team}
\begin{outerlist}
\item[] \href{http://www.ericsson.com/}{\textit{Ericsson China R\&D}}
        \hfill \textbf{2010}
\end{outerlist}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Professional Trainings %%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Trainings}
\textbf{Exerting the Influence in Project Management}
\begin{outerlist}
\item[] \href{http://www.ericssonacademy.com/}{\textit{Ericsson Academy, China}}
        \hfill \textbf{June 2011}
\end{outerlist}
\blankline

\textbf{On The Way To Lead}
\begin{outerlist}
\item[] \href{http://www.ericssonacademy.com/}{\textit{Ericsson Academy, China}}
        \hfill \textbf{June 2010}
\end{outerlist}
\blankline

\textbf{Manager Recruitment Training}
\begin{outerlist}
\item[] \href{http://www.ericssonacademy.com/}{\textit{Ericsson Academy, China}}
        \hfill \textbf{May 2010}
\end{outerlist}
\blankline

\textbf{Effective Java and Design Patterns}
\begin{outerlist}
\item[] \href{http://www.informator.se/}{\textit{Informator, Sweden}}
        \hfill \textbf{February 2010}
\end{outerlist}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Social Skills %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Social Skills}
{\textbf{Strong leader and full of team spirit}}\\
{\textbf{Excellent communicator}}\\
{\textbf{Travel on demand}}\\
{\textbf{Cope with pressure}}\\
{\textbf{Willing to learn new technology}}\\
{\textbf{Fluent in English and Chinese}}\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Knowledge Areas %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Knowledge Areas}
{\textbf{Web 2.0 and cutting-edge technologies}}\\
{\textbf{Problem identify and resolve}}\\
{\textbf{Distributed systems}}\\ 
{\textbf{Network security}}\\ 
{\textbf{OSI Model and network communication protocols}}\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Professional Skills%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Professional Skills} 
%
{\textbf{8 Years of Java Programming Experience:}}\\
Expert at Java EE/ Java SE/ Java ME

\blankline

{\textbf{4 Years of Ruby \nolinebreak on \nolinebreak Rails Experience:}}\\
Expert at 
\href{http://www.ruby-lang.org/en/}{Ruby}, 
\href{http://rubyonrails.org/}{Ruby on Rails} and RoR plugin hacking

\blankline

{\textbf{Database development and Management:}}\\
\href{http://www.mysql.com/}{MySQL}, 
\href{http://www.oracle.com/us/products/database/index.html}{Oracle Database}, 
\href{http://memcached.org/}{Memcached} and knowledge of NoSQL

\blankline

{\textbf{Java Frameworks:}}\\
JSF, Hibernate, EJB, Spring, Struts, GWT, Swing, JUnit, TestNG, Log4j, SLF4J

\blankline

{\textbf{Ruby \nolinebreak on \nolinebreak Rails plugin:}}\\
\href{http://activescaffold.com/}{ActiveScaffold},
Restful Authentication,
Cache Money,
Seed Fu

\blankline

{\textbf{Skill set of Web Services development:}}\\
SOAP, WSDL, UDDI, BPEL, Metro, AXIS, RESTful Web Service


\blankline

{\textbf{Skill set of Web Site development:}}\\
XHTML, XHTML MP, HTML, CSS, XML, Javascript, JSON, AJAX, JSP, PHP 

\blankline

{\textbf{Application Server:}}\\
Apache Tomcat, Jetty, Glassfish, JBoss, 
\href{http://nginx.net/}{nginx}, Apache HTTP Server

\blankline

{\textbf{Software Development Concept:}}\\
Agile Software Development 
(\href{http://en.wikipedia.org/wiki/Scrum_\%28development\%29}{Scrum}, 
\href{http://www.extremeprogramming.org/}{Extreme Programming}), Object-oriented Programming, UML, Design \nolinebreak Patterns

\blankline

{\textbf{Project management and team collaboration tools:}}\\
\href{http://maven.apache.org/}{Apache Maven},
\href{http://ant.apache.org/}{Apache Ant}, 
\href{http://git-scm.com/}{Git}, \href{http://www-01.ibm.com/software/awdtools/clearcase/index.html}{Rational\textregistered\space ClearCase (Base ClearCase and ClearCase UCM)},
\href{http://mercurial.selenic.com/}{Mercurial},
\href{http://subversion.tigris.org/}{Subversion}, 
\href{http://www.nongnu.org/cvs/}{CVS},
\href{http://jenkins-ci.org/}{Jenkins/Hudson},
\href{http://www.open.collab.net/products/ctf/}{CollabNet TeamForge},
\href{https://jazz.net/projects/rational-team-concert/}{Rational Team Concert}

\blankline

{\textbf{Development Tools:}}\\
\href{http://www.jetbrains.com/idea/}{IntelliJ\textregistered\space IDEA},
\href{http://www.jetbrains.com/ruby}{RubyMine\texttrademark},
\href{http://www.eclipse.org/}{Eclipse},
\href{http://netbeans.org/}{NetBeans IDE}, \\
\href{http://www.ibm.com/developerworks/rational/products/rsa/}{IBM\textregistered\space Rational\textregistered\space Software Architect (RSA)},
\href{http://www.embarcadero.com/products/jbuilder}{JBuilder}

\blankline

{\textbf{Other Programming Experience:}}\\
C/C++, PHP, Erlang, Prolog, DOT language

\blankline

{\textbf{Documentation Tools:}}\\ 
Microsoft Office, iWork, \LaTeX{}, 
and other common productivity packages for Windows, Mac\nolinebreak\space OS\nolinebreak\space X, and
Linux platforms

\blankline

{\textbf{Operating Systems:}}\\
Windows, Linux, Unix, Mac OS X\\
