% ********** Chapter 1 **********
\chapter{Background}
\label{sec:Background}

\lettrine[lines=3]{T}{his} chapter contains the background of \textsf{Web Call Example Application} as well as the task of the project. This chapter also explains the relationship between Web Call Example Application and its predecessor project \textsf{Web Call SDK}. Terminologies are also covered in this chapter.  

\section{Background}
\label{sec:Background:Background}

The technology of Voice over Internet Protocol (VoIP) enables communications services go through Internet. And it is on its way of taking the place of the traditional PSTN telephone network, especially in the domain of long distance or international phone calls. The market of VoIP is getting larger and larger. As the world-leading supplier in telecommunications, Ericsson realizes that the position of VoIP technology in the future of telecom industry is absolutely outstanding. To get the potential huge amount of customers, a project named Web Call Example Application(former \textit{Web Call SDK}) is planned by the department of Ericsson Developer Connection. The design goal is to create a web application that makes phone to phone VoIP calls. 

\section{Task}
\label{sec:Introduction:Task}

The task is to take all the benefits of VoIP and create a powerful application for phone calls. The application should be simple, stable, reusable, extendable, easy to access and user friendly. 

It should be a splendid application that supplies the function for users to make a phone call anytime, anywhere and to anyone in this world.



\section{Terminology}
\label{sec:Terminology}

\input{terminology/terminology.tex}
\clearpage
\section{About}
\label{sec:Introduction:Background:About}

\textbf{Web Call Example Application} is an open source project at \href{http://www.ericsson.com/developer/}{Ericsson Developer Connection}\footnote{Ericsson Developer Connection (former Ericsson Mobility World Developer Porgram) is a department of Ericsson. It helps developers to create applications that incorporate telecommunication network capabilities, such as location-based services, charging, messaging and presence, with sustainability in mind.} (EDC), \href{http://www.ericsson.com/}{Ericsson}\footnote{Ericsson is a world-leading provider of telecommunications equipment and related services to mobile and fixed network operators globally.}. It is the successor project of \textbf{Web Call SDK} \cite{WebCallSDK} which is developed by Yuening Chen at Ericsson AB during the year 2007 and 2008. After Yuening finished Web Call SDK, the people at EDC found it is not stable enough and many of the functions are not usable. So they decided to start a new project follow Web Call SDK to make the it stable and add some new features to it. The new project is called \textbf{Web Call Example Application}. As the main developer, I took over the new project at March 2008 and finished it at February 2009. I rewrite most code of the old project to make it stable and runnable and added some new features to it. As a result, the \textbf{Web Call Example Application} is used as the base library of Ericsson's demo of \textbf{Using REST and Web Services to Mash Up Communications Capabilities} \cite{DemoAtJavaOne} \cite{EricssonJavaOne} at \href{http://java.sun.com/javaone/}{JavaOne}\texttrademark\footnote{JavaOne is an annual conference (since 1996) put on by Sun Microsystems to discuss Java technologies} 2009.
% ********** End of chapter **********
